Planck and the Extra-terrestrials\\ or what the new SI means for astronomy

### 2020-04-10 spg/main.tex
bbl
adding more

In the 120 years since Planck speculated about it, we have yet to make
contact with non-human or extra-terrestrial cultures, and ask them if
they indeed share Planck's views on units.  What {\em has} happened,
however, is that physical constants have turned out to have meanings
not even Planck in 1899 had imagined.  As we all know, the following
year Planck himself discovered that $h$ (formerly known as $b$) was
about quantization.  A few years later the formal relation between
mass and energy through $c^2$ turned out to be real.  Starting in the
1920s $(\hbox{Planck mass})^{-2}\times(\hbox{proton mass})^3$ was
discovered to be the mass scale of stars.  Later in the 20th century,
$2e/h$ and $h/e^2$ turned out to be macroscopically observable as
Josephson's constant and von~Klitzing's constant.  And just in the
last few years, $c^5/G$ has been observed to be the power-output scale
for merging black holes.  We can only wonder what more surprises await
us.

@@

\bibliographystyle{apsrev4-1}
\bibliography{refs.bib}

>>>>

Solar grav lens.\cite{2020arXiv200211871T}

$\alpha_\odot=4GM_\odot/(c^2 R_\odot)$.  $R_\odot\approx
c\times2\unit{s}$.  Comes to $\approx10^{-5}\unit{radians}$.

Caustic at $R_\odot/\alpha_\odot$.  This is $\approx
c\times2\times10^5\unit{s}$ or $400\unit{au}$.  (Actually
$550\unit{au}$.)

$$ g_{\odot/\oplus} \approx 6\times10^{-3}\unit{m}\unit{s}^{-2} $$
$$ P_{\odot/\oplus} \approx 5\times10^{-6}\unit{Pa} $$

Would need $\approx 10^3\unit{m}^2\unit{kg}^{-1}$ to make the sun a
net repeller.

Cunning hybrid.

In the 120 years since Planck speculated about it, we have yet to make
contact with non-human or extra-terrestrial cultures, and ask them if
they indeed share Planck's views on units.  What {\em has} happened,
however, is that physical constants have turned out to have meanings
not even Planck in 1899 had imagined.  As we all know, the following
year Planck himself discovered that $h$ (formerly known as $b$) was
about quantization.  A few years later the formal relation between
mass and energy through $c^2$ turned out to be real.  Starting in the
1920s $(hc/G)^{-2}\times(\hbox{proton mass})^3$ was
discovered to be the mass scale of stars.  Later in the 20th century,
$2e/h$ and $h/e^2$ turned out to be macroscopically observable as
Josephson's constant and von~Klitzing's constant.  And just in the
last few years, $c^5/G$ has been observed to be the power-output scale
for merging black holes.  We can only wonder what more surprises await
us.

@@

\bibliographystyle{apsrev4-1}
\bibliography{main.bbl}
